Applications of limited information strategies in Menger's game

### 2015-09-25 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
finished except for abstract/intro

\begin{definition}
  A subset \(Y\) of \(X\) is \term{relatively compact} to \(X\) if for every open
  cover of \(X\), there exists a finite subcollection which covers \(Y\).
\end{definition}

\begin{proposition}
  For regular spaces, \(Y\) is relatively compact to \(X\) if and only if
  \(\cl Y\) is compact in \(X\).
\end{proposition}

%TODO cite source?

@@

\begin{theorem}[\(\alcompS{\mf c}\)]
  \(\pl F\kmarkwin2\menGame{R_\omega}\).
\end{theorem}

>>>>

\begin{definition}
  A subset \(Y\) of \(X\) is \term{relatively compact} to \(X\), or
  \(Y\) is \term{compact in} \(X\), if for every open
  cover of \(X\), there exists a finite subcollection which covers \(Y\).
\end{definition}

\begin{definition}
  A subset \(Y\) of \(X\) is \term{precompact} in \(X\) if
  \(\text{cl}_X(Y)\) is compact.
\end{definition}

Some authors use the term
relative compactness to denote precompactness, which causes
no confusion in the context of regular spaces.

\begin{proposition}
  For regular spaces, \(Y\) is relatively compact to \(X\) if and only if
  \(Y\) is precompact in \(X\).
\end{proposition}

\begin{proof}
  Shown by Arhangel'skii in \cite{MR1885790}; a proof is provided for the
  convenience of the reader.

  Let \(\mc U=\{U_\alpha:\alpha<\kappa\}\) be an
  open cover of \(\text{cl}_X(Y)\); for \(y\in Y\), apply regularity to get
  \(V_\alpha\subseteq\text{cl}_X(V_\alpha)\subseteq U_\alpha\)
  with \(V_\alpha\) open.
  Use relative compactness to obtain a finite subcollection of
  \(\{X\setminus\text{cl}_X(Y)\}\cup\{V_\alpha:\alpha<\kappa\}\)
  covering \(Y\): \(\{V_{\alpha_i}:i<n\}\). Then since
  \(\bigcup\{\text{cl}_X(V_{\alpha_i}):i<n\}\) is a closed set in \(X\)
  containing \(Y\), it contains \(\text{cl}_X(Y)\), and thus
  \(\{U_{\alpha_i}:i<n\}\) is a finite subcollection of \(\mc U\) covering
  \(\text{cl}_X(Y)\).

  For the reverse direction, simply take a finite subcover of
  \(\text{cl}_X(Y)\) to obtain a finite subcover of \(Y\).
\end{proof}

@@

\begin{theorem}
  Assuming \(CH\) or just \(\alcompS{\mf c}\),
  \(\pl F\kmarkwin2\menGame{R_\omega}\).
\end{theorem}
